%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Main Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Spring boot, Java, Kotlin, React, Node, Redis} % Languages
    {PagoPA Checkout} % Project name
    {July 2024 - April 2025} % Location
    {BV TECH S.p.A.} % Organization
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and enhanced all components of the payments platform, focusing on both \textbf{frontend} and \textbf{backend} performance optimization.}
        \item {Developed \textbf{unit tests} to ensure full coverage of \textbf{React} components, improving code reliability and maintainability.}  
        \item {Optimized the Wallet API by integrating \textbf{Redis caching}, achieving an \textbf{60\% reduction} in response time.}  
        \item {Implemented an \textbf{authentication flow using SPID}, the Italian digital identity system, to ensure secure user access.}  
        \item {Designed \textbf{CI pipelines} for automated deployments, including \textbf{unit and integration testing} across UAT and production environments.}  
        \item {Perfomed \textbf{soak testing} using K6 to validate the stability and performance of \textbf{Node.js microservice} after the upgrade to version 22.}  
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java, Spring boot} % Languages
    {Ministero di Giustizia} % Project name
    {Jan 2024 - July 2024} % Location
    {Exaltech S.r.l.} % Organization
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The website serves as the \textbf{official portal for public sales} related to judicial auctions in Italy.}
        \item {\textbf{Designed and implemented} a process for receiving telematic offers from prospective buyers in judicial sales.}
        \item {Developed a system to read certified electronic mail (PEC) and \textbf{securely store encrypted offers}, which are automatically decrypted and opened three hours prior to the scheduled judicial hearing.}  
        \item {\textbf{Managed external communications} and outcome reporting through SOAP-based web services, ensuring compliance with legal and procedural standards.}  
        \item {\textbf{Orchestrated process execution} using batch jobs that \textbf{concurrently} access the database, monitoring and updating the status of individual workflows.}  
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Javascript, AngularJS, Cordova, Camunda} % Languages
    {Smactory} % Project name
    {May 2016 - July 2024} % Location
    {Exaltech S.r.l.} % Organization
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{SMACTORY} is a set of intuitive solutions, able to get you more information in real time about the status of your machinery, processes and human-machine interactions.}
        \item {The platform integrates advanced features such as \textbf{augmented reality}, \textbf{beacon detection}, \textbf{QR code scanning}, and \textbf{video calling} to enhance user experience and operational efficiency.}  
        \item {\textbf{Designed and developed} a responsive web application compatible with \textbf{all devices}, using a single codebase. The application was converted into a hybrid mobile app using the Cordova framework.}  
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
