%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Development Sr. Specialist} % Job title
    {BV TECH S.p.A.} % Organization
    {Remote} % Location
    {July 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Software development consultant at PagoPA. Main activity involves optimizing existing payment processes and adding new features to improve user experience and increase platform efficiency. The agile framework Scrum was used for development.}
        \item {Development of communications management software for the Lombardy region.}  
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Exaltech S.r.l.} % Organization
    {Latina} % Location
    {May 2013 - July 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mobile applications design and development (Hybrid).}
        \item {Web-based applications design and development.}  
        \item {Android applications design and development.}  
        \item {User Interface Design.}  
        \item {Back-end development.}  
        \item {Brochures design for the marketing department}  
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ICT security consultant} % Job title
    {Black Sun Factory S.r.l } % Organization
    {Pomezia} % Location
    {Feb. 2013 - May 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Antivirus migration activities and troubleshooting of about 6000 MIUR PDLs throughout Italy.}
        \item {The main activity carried out concerns the analysis of the main malware in circulation.
              After having analyzed all their functions and the dangers that an hypothetical infected
              user incurs, everything is reported in a document (written in English) with the addition of
              the mitigation procedure of the affected system.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
