%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Main Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Spring boot, Java, Kotlin, React, Node, Redis} % Languages
    {PagoPA Checkout} % Project name
    {July 2024 - April 2025} % Location
    {BV TECH S.p.A.} % Organization
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and enhanced all components of the payments platform, focusing on both frontend and backend performance optimization.}
        \item {Developed unit tests to ensure full coverage of React components, improving code reliability and maintainability.}  
        \item {Optimized the Wallet API by integrating Redis caching, achieving an 60\% reduction in response time.}  
        \item {Implemented an authentication flow using SPID, the Italian digital identity system, to ensure secure user access.}  
        \item {Designed CI pipelines for automated deployments, including unit and integration testing across UAT and production environments.}  
        \item {Perfomed soak testing using K6 to validate the stability and performance of Node.js microservice after the upgrade to version 22.}  
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java, Spring boot} % Languages
    {Ministero di Giustizia} % Project name
    {Jan 2024 - July 2024} % Location
    {Exaltech S.r.l.} % Organization
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The website serves as the official portal for public sales related to judicial auctions in Italy.}
        \item {Designed and implemented a process for receiving telematic offers from prospective buyers in judicial sales.}
        \item {Developed a system to read certified electronic mail (PEC) and securely store encrypted offers, which are automatically decrypted and opened three hours prior to the scheduled judicial hearing.}  
        \item {Managed external communications and outcome reporting through SOAP-based web services, ensuring compliance with legal and procedural standards.}  
        \item {Orchestrated process execution using batch jobs that concurrently access the database, monitoring and updating the status of individual workflows.}  
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Javascript, AngularJS, Cordova} % Languages
    {Smactory} % Project name
    {May 2016 - July 2024} % Location
    {Exaltech S.r.l.} % Organization
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {SMACTORY is a set of intuitive solutions, able to get you more information in real time about the status of your machinery, processes and human-machine interactions.}
        \item {The platform integrates advanced features such as augmented reality, beacon detection, QR code scanning, and video calling to enhance user experience and operational efficiency.}  
        \item {Designed and developed a responsive web application compatible with all devices, using a single codebase. The application was converted into a hybrid mobile app using the Cordova framework.}  
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
